---
title: 'DS 202: Lab 3'
author: "MyTien Kien; kmytien"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Uploading Data
```{r}
#Shows warnings?
dat <- readxl::read_xls('C:\\Users\\kmyti\\OneDrive\\Desktop\\excel_files_202\\GSS.xls')
```

##### 1. Find the average years of education for the respondents with each marital status. Arrange your output in a meaningful order and print. Describe any patterns you find.

```{r}

```


##### 2. Create a single data frame containing records for the better educated respondents with each marital status. A “better educated” respondent is someone who has strictly more years of education than the average among those with the same marital status. Print the structure of the data frame.

```{r}

```


##### 3. How is the happiness of a respondent related to his/her marriage status? Define that a person is happy if the response to question is “Very happy” or “Pretty happy”.

```{r}

```


##### 4. Does party affiliation affect the relationship you found in the last question?

```{r}

```


##### 5. How is marital status related to the education of a respondent? What are possible reasons accounting for the patterns you see?

```{r}

```


##### 6. Explore two more interesting questions, and answer those questions using the GSS data.

```{r}

```

