---
title: 'DS 202: Lab 3'
author: "MyTien Kien; kmytien, Tanner Dunn; tcdunn"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Uploading Data
```{r}
#Shows warnings?
library(tidyverse)
dat <- readxl::read_xls('C:/Spring2021/ds202/Lab3/GSS.xls')
dat1 <- rename(dat, 'work_hours' = 'Number of hours usually work a week',
               'marital' = 'Marital status',
               'education' = 'Highest year of school completed',
               'gender' = 'Respondents sex',
               'num_household' = 'Number of persons in household',
               'party_affiliation' = 'Political party affiliation',
               'happiness' = 'General happiness')
dat1 <- filter(dat1, education != "No answer")

head(dat1)
```

##### 1. Find the average years of education for the respondents with each marital status. Arrange your output in a meaningful order and print. Describe any patterns you find.

```{r}

```


##### 2. Create a single data frame containing records for the better educated respondents with each marital status. A “better educated” respondent is someone who has strictly more years of education than the average among those with the same marital status. Print the structure of the data frame.

```{r}
better_educated <- dat1 %>%
    select(marital, education) %>%
    group_by(marital) %>%
    filter(education > mean(education, na.rm = TRUE)) %>%
    arrange(marital)

str(better_educated)

```


##### 3. How is the happiness of a respondent related to his/her marriage status? Define that a person is happy if the response to question is “Very happy” or “Pretty happy”.

```{r}

```


##### 4. Does party affiliation affect the relationship you found in the last question?

```{r}

```


##### 5. How is marital status related to the education of a respondent? What are possible reasons accounting for the patterns you see?

```{r}

```


##### 6. Explore two more interesting questions, and answer those questions using the GSS data.

```{r}

```

